NanoMaLy

### 2015-11-19 paper/pldi16-submission/interactive.tex
down to 11pp

Next, we present a novel way to debug executions.
%
First, we develop a notion of a
\emph{reduction graph}~(\S~\ref{sec:reduction-graph}).
%
Second, we extend our semantics so that they incrementally
collect the edges in the graph (\S~\ref{sec:inter-semant}).
%
Finally, we express a set of common debugging steps as
graph traversals (\S~\ref{sec:traversing-graph}), yielding
an novel visual interactive debugger that allows the user
to effectively visualize \emph{how} the program goes (wrong.)

@@

@@

\subsection{Traversing the Reduction Graph}
\label{sec:traversing-graph}
Given a reduction graph $G$ and an initial path
$p = \singlestep{e_1}{\singlestep{e_2}{e_n}}$, such that
\stepsg{e_1}{\emptysu}{\bullet}{e_n}{\su}{\tr}, we define the following
traversals in Figure~\ref{fig:traversing-graph}:
%
\begin{itemize}
\item \stepforwardsym takes a single step forward.
\item \stepbackwardsym takes a single step backward.
\item \jumpforwardsym takes a ``big'' step forward to the next function call.
\item \jumpbackwardsym takes a ``big'' step backward to the previous function call.
\item \stepintosym steps into a function call in a sub-term, isolating it from the context.
\item \stepoversym steps over a function call in a sub-term.
\end{itemize}
%
The initial path $p$ is required for the backward-steps as a node may
have multiple incoming $\leadsto$ edges, \eg
\singlestep{\eplus{1}{2}}{3} and \singlestep{\eplus{2}{1}}{3}.
%
The sub-term edges $\searrow$ allow us to decompose an expression into a
sub-expression and the surrounding context, thus enabling the \stepintosym
and \stepoversym traversals.
%

>>>>

Next, we present a novel way to debug executions.
%
First, we develop a notion of a
\emph{reduction graph}~(\S~\ref{sec:reduction-graph}).
%
Second, we extend our semantics with a form of \emph{tracing}
so that they incrementally collect the edges in the graph
(\S~\ref{sec:inter-semant}).
%
Finally, we express a set of common \emph{interactive debugging}
steps as graph traversals (\S~\ref{sec:traversing-graph}), yielding
an novel visual interactive debugger that allows the user
to effectively visualize \emph{how} the program goes (wrong.)

@@

\subsection{Reduction Graphs}

@@

% \subsection{Traversing the Reduction Graph}
\subsection{Interactive Debugging}
\label{sec:traversing-graph}

Given a reduction graph $G$ and an initial path
$p = \singlestep{e_1}{\singlestep{e_2}{e_n}}$, such that
\stepsg{e_1}{\emptysu}{\bullet}{e_n}{\su}{\tr}, we define the following
traversals in Figure~\ref{fig:traversing-graph}:
%
\begin{itemize}
\item \stepforwardsym takes a single step forward.
\item \stepbackwardsym takes a single step backward.
\item \jumpforwardsym takes a ``big'' step forward to the next function call.
\item \jumpbackwardsym takes a ``big'' step backward to the previous function call.
\item \stepintosym steps into a function call in a sub-term, isolating it from the context.
\item \stepoversym steps over a function call in a sub-term.
\end{itemize}
%
The initial path $p$ is required for the backward-steps as a node may
have multiple incoming $\leadsto$ edges, \eg
\singlestep{\eplus{1}{2}}{3} and \singlestep{\eplus{2}{1}}{3}.
%
The sub-term edges $\searrow$ allow us to decompose an expression into a
sub-expression and the surrounding context, thus enabling the \stepintosym
and \stepoversym traversals.
%
